Human Capital Model

### 2015-02-09 paper.tex
Update paper

At time $t$, we choose top 10\% of the employees which have the
properties above and decrease their churn rate by 50\%. As shown in
Figure\ref{}, the churn rate decrease rapidly.

@@

\begin{equation}
  \begin{split}
  \min&\sum_{i=1}^n\sum_{j=1}^m m_{ij}x_{ij} \\
  s.t.& \sum_{j=1}^m x_{ij}=1, i=1,2,\ldots,n \\
  &\sum_{i=1}^n x_{ij} \le1,j=1,2,\ldots,m \\
  &x_{ij}=0 \mbox{or} 1,i=1,2,\ldots,n,j=1,2,\ldots,m
  \end{split}
\end{equation}

@@

\begin{figure}[center]
  \centering

  \caption{Productivity-Time Curve}\label{reassign}
\end{figure}

@@

This part shows how our model connects to other organizational network
layers such as information flow, trust, influence, and
friendship. Number the layers from 0 to
k. $$G^\alpha=(V^\alpha,E^\alpha), \alpha=1,2,\ldots,k$$ Each
$E^\alpha$ is colored by a specific color. $G^0$ reprensents the
network we built before, $G^1$, $G^2, \ldots ,G^k$ represent the other layers added.

>>>>

At time $t$, we choose top 10\% of the employees which have the
properties above and decrease their churn rate by 50\%. As shown in
Figure\ref{churn-rate}, the churn rate decrease rapidly.

\begin{figure}[htb]
  \centering
  \includegraphics[width=11cm]{p4.pdf}
  \caption{Churn rate-Time Curve}
  \label{churn-rate}
\end{figure}

@@

\begin{equation}
  \begin{split}
  \min&\sum_{i=1}^n\sum_{j=1}^m m_{ij}x_{ij} \\
  s.t.& \sum_{j=1}^m x_{ij}=1, i=1,2,\ldots,n \\
  &\sum_{i=1}^n x_{ij} \le1,j=1,2,\ldots,m \\
  &x_{ij}=0 \mbox{ or } 1,i=1,2,\ldots,n,j=1,2,\ldots,m
  \end{split}
\end{equation}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=11cm]{p3.pdf}
  \caption{Productivity-Time Curve}\label{reassign}
\end{figure}

@@

This part shows how our model connects to other organizational network
layers such as information flow, trust, influence, and
friendship. Number the layers from 0 to
k. $$G^\alpha=(V^\alpha,E^\alpha), \alpha=1,2,\ldots,k$$ Each
$E^\alpha$ is colored by a specific color. $G^0$ reprensents the
network we built before, $G^1, G^2, \ldots ,G^k$ represent the other layers added.
